\textbf{ZKLoRA: Efficient Zero-Knowledge Proofs for LoRA Verification}

### 2025-01-17 paper/main.tex
edit footnote text

We benchmarked \texttt{ZKLoRA} across several LLMs and smaller models with different numbers of LoRA modules. 
Our central question is how verification times, as well as settings and proof generation times, grow with \textbf{the number of LoRA modules}, while also considering each LoRA's average parameter size. 
Figure~\ref{fig:verify_vs_numlora} and Table~\ref{tab:settings_proof} detail this trade-off. \footnote{Note that the number of LoRA modules in a given model is not purely a function of number of layers -- it is also a choice of which weight matrices within each layer is targeted. For example, just targeting one matrix per layer (ie the Query matrix in the Attention Block) will yeild one LoRA per layer, but, for example targeting the Query, Key, and Value matrices yeild three matrices per layer and makes the total number of LoRAs $3 \times num$\_$layers$.}

>>>>

We benchmarked \texttt{ZKLoRA} across several LLMs and smaller models with different numbers of LoRA modules. 
Our central question is how verification times, as well as settings and proof generation times, grow with \textbf{the number of LoRA modules}, while also considering each LoRA's average parameter size. 
Figure~\ref{fig:verify_vs_numlora} and Table~\ref{tab:settings_proof} detail this trade-off. \footnote{Note that the number of LoRA modules in a given model is not purely a function of the number of layers -- it is also a choice of which weight matrices within each layer is targeted. For example, just targeting one matrix per layer (ie the Query matrix in the Attention Block) will yeild one LoRA per layer. Conversely, targeting the Query, Key, and Value matrices yields three matrices per layer and makes the total number of LoRAs $3 \times num$\_$layers$.}
